---
title: "Main page"
output: 
  html_document: 
    df_print: paged
---

## Tidy Tuesdays

21st September 2021

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE)
library(tidyverse)
library(jsonlite)
library(httr)
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)# for more themes (including theme_map())
library(knitr)
theme_set(theme_minimal())
```


```{r cars}
# In this code chunk, I am loading in the tidy tuesday Billboard data 

tuesdata <- tidytuesdayR::tt_load('2021-09-14')
tuesdata <- tidytuesdayR::tt_load(2021, week = 38)

billboard <- tuesdata$billboard
audio_features <- tuesdata$audio_features
```

```{r}
# In this code chunk, I find the performers who have performed the highest number of songs, which will allow me to choose a performer to use for my graph.
top_performer <- audio_features %>%
  group_by(performer) %>% 
  summarise(number_songs = n()) %>% 
  arrange(desc(number_songs)) %>% 
  head(6) %>% 
  view()
```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
# In this chode chunk, I am creating a ggplot scatterplot depicting popularity vs danceability
audio_features %>% 
  filter(performer == "Taylor Swift") %>% 
  ggplot(aes(x = danceability, 
             y = spotify_track_popularity)) +
  geom_point(fill = "red") +
  labs(title = "Are Taylor Swift's Danceable Songs Generally More Popular?", 
       x = "Danceability of Song",
       y = "Spotify Popularity of Song") +
  geom_smooth(method = lm)
```


The question that my graph is trying to answer is: 
*Are Taylor Swift's Danceable Songs Generally More Popular?*
This graph helps me answer this question, since I can see a positive trend line when plotting the 'danceability' variable against the 'Spotify popularity' variable of the data set. I decided to explore this question for today's assignment because I have enjoyed Taylor Swift's music since I was a tween, and enjoyed both her upbeat dance songs and relaxed acoustic songs, which made me wonder whether certain types of songs were generally more popular.  

